A Framework for Predictable Actor-Critic Control

### 2022-05-09 documentation/old_paper_format.tex
indent

\begin{document}
\maketitle

% # What is the design of the agent?

% There are three tasks that the agent needs to address for bounded-loss planning; choosing an action, determining the value of a state-action pair, and predicting future states. The first two tasks can easily be addressed with the actor and critic respectively from a standard SAC design. For the planning task, a separate dynamics model is used. While these are specific choices, the principle should hold for any agent capable of those three tasks.

% # Present theoretical bound

% To gain a theoretical bound on this approach, 
% ToDo: Make a tree of possible options

% # How to choose an Epsilon?

% The value of epsilon is extremely impactful but also non-linear
% Epsilon acts as a non-linear trade-off between commitment and performance. Applications, such as predictability of a single vehicle, or predictability of millions of cellular agents, can desire very different points on the trade-off curve.

% Additionally, while theoretical bounds are useful, we've found performance to be significantly above the theoretical lower bound. Therefore, to get an optimal trade-off, we must calculate an epsilon for each environment and each agent.

% Algorithm 1 allows the user to select the amount of per-episode degradation, and then generate an epsilon that approximately achieves that target. In particular, the algorithm is designed to quickly converge despite high variance in environments and agents.

% - switch to % based method for epsilon

% However,

% as a general technique

%  to stabilize our metrics,

% First, the application is the ultimate dictator of what epsilon

% While theoretical bounds are very convenient,

% While the application might dictate the value of epsilon, it is worthwhile to

% This is of critical importance to 
% How will success be measured?

% The two key metrics are plan-commitment-length, and total episode reward. Six techniques are compared across 4 environments. In future work it would be worthwhile to add multi-agent environments with an aggregate reward metric. The metrics chosen here are intended to establish a precedent for such work.

% The environments are lunar lander continuous v0, ant bullet v0, half cheetah bullet, and humanoid v0 (CHECK). The six techniques consistent of two trivial methods; 0-length commitment,  and infinite-length commitment, the experimental method PrAC, and three methods from (FIXME imaginary trajectory reference), which are N-Step, First Step Alike (FSA), and Confidence Bounds (CB).

\begin{abstract}

Reinforcement learning (RL) algorithms commonly provide a one action plan per time step. Doing this allows the RL agent to quickly adapt and respond to stochastic environments yet it restricts the ability to predict the agent's future behavior. This paper proposes an actor-critic framework that predicts and follows an $n$-step plan. Committing to the next $n$ actions presents a trade-off between behavior predictability and reduced performance. In order to balance this trade-off, a dynamic plan-following criteria is proposed for determining when it is too costly to follow the preplanned actions and a replanning procedure should be initiated instead. 
Performance degradation bounds are presented for the proposed criteria when assuming access to accurate state-action values. Experimental results, using several robotics domains, suggest that the performance bounds are also satisfied in the general (approximation) case on expectancy. Additionally, the experimental section presents a study of the predictability versus performance degradation trade-off and demonstrates the benefits of applying the proposed plan-following criteria.

\end{abstract}

@@

\begin{algorithm}[h]
% \SetAlgoLined\
\SetKwInOut{Input}{Input}
\SetKwInOut{Output}{Output}
\Input{
    multiplier for epsilon $\mathrm{inc}$,\\
    baseline min confidence interval $\mathrm{b_{min}}$,\\
    confidence interval $\mathrm{ci_{lvl}}$,\\
    minimum average episode reward $\mathrm{b_{lower}}$,\\
    baseline confidence interval width $\mathrm{b_{ci}}$,\\
    number of baseline samples $\mathrm{b_{sz}}$,\\
    initial epsilon $\mathrm{\epsilon_{i}}$,\\
    initial horizon $\mathrm{h_{i}}$,\\
    number of iterations of refinement $\mathrm{iter}$\\    
}
\Output{
    \\
    a refined epsilon $\mathrm{\epsilon_{i}}$
    a refined horizon $\mathrm{h_{i}}$
}
\caption{Refine2}
\label{algo:replan2}

Initialize an empty array $ epsilon\_attempts $
Initialize an empty hash map $ planlens_\epsilon $. Requesting a non-existent key for $ planlens_\epsilon $ returns an array containing $h_i$

\For{$i$ in $[0,..., iter]$}{
    \label{ln:loopplan1}
    Initialize an empty array $sampled\_rewards$ 
    $a \gets 10$ 
    \For{$i$ in $[0,..., b_{sz}]$}{
        \label{ln:loopsample1}
        $discounted\_rewards, planlens 
             \gets run\_episode(\epsilon=e_n)$ 
        $sampled\_rewards.push(\sigma(discounted\_rewards))$ 
        $planlens_\epsilon[\epsilon\_n] 
            \gets concat(planlens_\epsilon[\epsilon_i], planlens)$

        \If{$length(sampled\_rewards) < 2$} {
            $continue$
        }

        $s_{max}           \gets
        \hspace{0.5cm}    confidence\_interval\_upper(ci_{lvl}, sampled\_rewards)$
        $confidence\_size \gets
        \hspace{0.5cm}    confidence\_interval\_size(ci_{lvl} , sampled\_rewards)$
        \If{$s_{max} < baseline_{min} \leq confidence_size < b_ci$}{
            $break$
        }
    }

    \If{$mean(sampled\_rewards) \geq b_{lower}$}{
        $\epsilon_n \*= inc$
    }{
        $\epsilon_n \/= inc$
    }

    $epsilon\_attempts.push(\epsilon_n)$
}
$\epsilon_o = median(epsilon\_attempts)$

$h_o = max(median(planlens_\epsilon[\epsilon_o]), 1) * 2$

\Return{
    $\mathrm{\epsilon_{o}}$
    $\mathrm{h_{o}}$
}
\end{algorithm}

>>>>

\begin{document}
    \maketitle
    \begin{abstract}
        Reinforcement learning (RL) algorithms commonly provide a one action plan per time step. Doing this allows the RL agent to quickly adapt and respond to stochastic environments yet it restricts the ability to predict the agent's future behavior. This paper proposes an actor-critic framework that predicts and follows an $n$-step plan. Committing to the next $n$ actions presents a trade-off between behavior predictability and reduced performance. In order to balance this trade-off, a dynamic plan-following criteria is proposed for determining when it is too costly to follow the preplanned actions and a replanning procedure should be initiated instead. 
        Performance degradation bounds are presented for the proposed criteria when assuming access to accurate state-action values. Experimental results, using several robotics domains, suggest that the performance bounds are also satisfied in the general (approximation) case on expectancy. Additionally, the experimental section presents a study of the predictability versus performance degradation trade-off and demonstrates the benefits of applying the proposed plan-following criteria. 
    \end{abstract}

@@
